Model Search in Relational Domains

### 2016-10-21 deductions.tex
sync
section 5

Algorithm~\ref{Alg:ms} presents the deduction phase in abstract model
search procedure. \pscmt{The propagation heuristics $H$ provides two
  functions $\mathit{initialize\_worklist}$ and
  $\mathit{update\_worklist}$. Describe them for the different
  heuristics (already done for initialize, TBD for update...}
A {\em worklist} is a queue which contains \rmcmt{abstract deduction
transformers}.  A {\em worklist} is initialized following a heuristics 
choice for iteration strategies. A {\em forward} iteration 
strategy initializes the worklist with \rmcmt{abstract} transformers that 
has constants in the right-hand side. Whereas, a {\em backward} 
iteration strategy starts with a set of assertions. On the other hand, a 
{\em multi-way} iteration strategy initializes the worklist with set of all 
transformers and performs both forward and backward propagations in tandem.  
For every meet irreducible deduction transformer \pscmt{rename} $s \in S$ 
passed to the abstract domain, if the domain infers a new meet irreducible 
$\mathit{meet\_irrd}$, it is added to $\mathcal{T}$ \pscmt{It usually infers several ones.}.  Additionally, the reason 
trail $\mathcal{R}$ \pscmt{define} is updated with the transformer $s$ as the reason for inferring
$\mathit{meet\_irrd}$. If a conflict is deduced, that is, $\mathit{meet\_irrd} = \bot$ 
is inferred by the domain, the algorithm terminates with \textsf{conflict}.  However,
when a fixed-point is reached, the abstract valuation $v$ is checked for set of
models.  This is determined by checking whether the set of assignments in $v$ is 
$\gamma$-complete~\cite{dhk2013-popl}. If $v$ is $\gamma$-complete, that is, the 
abstract valuation $v$ is abstractly satisfying, the abstract model 
search terminates with \textsf{sat}.  Otherwise, the algorithm returns \textsf{unknown} and the 
model search procedure makes a new decision.

>>>>

Algorithm~\ref{Alg:ms} presents the deduction phase in abstract model
search procedure. \pscmt{The propagation heuristics $H$ provides two
  functions $\mathit{initialize\_worklist}$ and
  $\mathit{update\_worklist}$. Describe them for the different
  heuristics (already done for initialize, TBD for update...}
A {\em worklist} is a queue which contains \rmcmt{abstract deduction
transformers}.  A {\em worklist} is initialized following a heuristics 
choice for propagation strategies. A {\em forward} propagation strategy 
initializes the worklist with \rmcmt{abstract} transformers that 
has constants in the right-hand side. Whereas, a {\em backward} 
iteration strategy starts with a set of assertions. On the other hand, a 
{\em multi-way} iteration strategy initializes the worklist with set of all 
transformers and performs both forward and backward propagations in tandem.  
For every meet irreducible deduction transformer \pscmt{rename} $s \in S$ 
passed to the abstract domain, if the domain infers a new meet irreducible 
$\mathit{meet\_irrd}$, it is added to $\mathcal{T}$ \pscmt{It usually infers several ones.}.  Additionally, the reason 
trail $\mathcal{R}$ \pscmt{define} is updated with the transformer $s$ as the reason for inferring
$\mathit{meet\_irrd}$. If a conflict is deduced, that is, $\mathit{meet\_irrd} = \bot$ 
is inferred by the domain, the algorithm terminates with \textsf{conflict}.  However,
when a fixed-point is reached, the abstract valuation $v$ is checked for set of
models.  This is determined by checking whether the set of assignments in $v$ is 
$\gamma$-complete~\cite{dhk2013-popl}. If $v$ is $\gamma$-complete, that is, the 
abstract valuation $v$ is abstractly satisfying, the abstract model 
search terminates with \textsf{sat}.  Otherwise, the algorithm returns \textsf{unknown} and the 
model search procedure makes a new decision.
